---
title: "gg.tzh"
author: Tingting Zhan
format: 
  html:
    page-layout: full
    html-math-method: katex
toc: true
toc-location: left
toc-depth: 4
toc-title: ''
editor: visual
knitr:
  opts_chunk: 
    collapse: true
    comment: "#>" 
vignette: >
  %\VignetteIndexEntry{intro}
  %\VignetteEngine{quarto::html}
  %\VignetteEncoding{UTF-8}
---

# Introduction

This vignette of package **`gg.tzh`** ([Github](https://github.com/tingtingzhan/gg.tzh)) documents ...

## Note to Students

Examples in this vignette require that the `search` path has

```{r}
library(gg.tzh)
library(latex2exp)
```


```{r}
(col = scales::pal_hue()(n = 2L))
```

```{r}
#| echo: false
library(knitr) # for tables in this vignette
#options(mc.cores = 1L) # for CRAN submission
theme_bw() |> theme_set()
```


## Terms and Abbreviations

```{r}
#| echo: false
#| results: asis
c(
  '[`|>`](https://search.r-project.org/R/refmans/base/html/pipeOp.html)', 'Forward pipe operator introduced in `R` 4.1.0',
  '`$`', '[Extract](https://search.r-project.org/R/refmans/base/html/Extract.html) parts of an object',
  '[`abline`](https://search.r-project.org/R/refmans/graphics/html/abline.html)', 'Add straight line (by intercept and slope) to a plot',
  '[`aov`](https://search.r-project.org/R/refmans/stats/html/aov.html), [`anova`](https://search.r-project.org/R/refmans/stats/html/anova.html)', 'Analysis-of-variance (ANOVA) model; ANOVA table',
  '[`boxplot`](https://search.r-project.org/R/refmans/graphics/html/boxplot.html)', 'Box plot',
  '`CRAN`, `R`', '[The Comprehensive R Archive Network](https://cran.r-project.org)',
  '[`chisq.test`](https://search.r-project.org/R/refmans/stats/html/chisq.test.html)', 'Pearson\'s $\\chi^2$-test',
  '[`class`](https://search.r-project.org/R/refmans/base/html/class.html)', 'Object class',
  '[`confint`](https://search.r-project.org/R/refmans/stats/html/confint.html)', 'Confidence intervals for model parameters',
  '[`cut`](https://search.r-project.org/R/refmans/base/html/cut.html)', 'Convert numeric to factor',
  '[`data.frame`](https://search.r-project.org/R/refmans/base/html/data.frame.html)', 'Data frame',
  '[`dim`](https://search.r-project.org/R/refmans/base/html/dim.html)', 'Dimensions',
  '[`dbinom`, `pbinom`, `qbinom`](https://search.r-project.org/R/refmans/stats/html/Binomial.html)', 'Binomial density, probability, quantile',
  '[`dpois`, `ppois`, `qpois`](https://search.r-project.org/R/refmans/stats/html/Poisson.html)', 'Poisson density, probability, quantile',
  '[`dnorm`, `pnorm`, `qnorm`](https://search.r-project.org/R/refmans/stats/html/Normal.html)', 'Normal density, probability, quantile',
  '[`exp`](https://search.r-project.org/R/refmans/base/html/Log.html)', 'Exponential',
  '[`factor`](https://search.r-project.org/R/refmans/base/html/factor.html)', 'Factor',
  '[`fisher.test`](https://search.r-project.org/R/refmans/stats/html/fisher.test.html)', 'Fisher\'s exact test', 
  '[`glm`](https://search.r-project.org/R/refmans/stats/html/glm.html)', 'Generalized linear model',
  '[`head`, `tail`](https://search.r-project.org/R/refmans/utils/html/head.html)', 'First or last parts of an object',
  '[`kurtosis`](https://search.r-project.org/CRAN/refmans/e1071/html/kurtosis.html)', 'Kurtosis',
  '[`L`](https://adv-r.hadley.nz/vectors-chap.html#atomic-vectors)', '[Integer](https://search.r-project.org/R/refmans/base/html/integer.html) notation',
  '[`label_percent`](https://search.r-project.org/CRAN/refmans/scales/html/label_percent.html)', 'Label for percentages',
  '[`lm`](https://search.r-project.org/R/refmans/stats/html/lm.html)', 'Linear model',
  '[`log`](https://search.r-project.org/R/refmans/base/html/Log.html)', 'Logarithm',
  '[`matrix`](https://search.r-project.org/R/refmans/base/html/matrix.html)', 'Matrices',
  '[`mean`](https://search.r-project.org/R/refmans/base/html/mean.html)', 'Arithmetic mean',
  '[`median`](https://search.r-project.org/R/refmans/stats/html/median.html)', 'Median',
  '[`Mode`](https://search.r-project.org/CRAN/refmans/pracma/html/mode.html)', 'Mode',
  '[`names`](https://search.r-project.org/R/refmans/base/html/names.html)', 'Names of an object',
  '[`nrow`](https://search.r-project.org/R/refmans/base/html/nrow.html)', 'Number of rows',
  '[`ordered`](https://search.r-project.org/R/refmans/base/html/factor.html)', 'Ordered factor',
  '[`plot`](https://search.r-project.org/R/refmans/base/html/plot.html)', 'Plot',
  '[`prop.test`](https://search.r-project.org/R/refmans/stats/html/prop.test.html)', 'Pearson\'s $\\chi^2$-test on proportions',
  '[`quantile`](https://search.r-project.org/R/refmans/stats/html/quantile.html)', 'Quantile',
  '[`rep`](https://search.r-project.org/R/refmans/base/html/rep.html)', 'Replicate elements',
  '[`sample`, `sample.int`](https://search.r-project.org/R/refmans/base/html/sample.html)', 'Random samples', 
  '[`sd`](https://search.r-project.org/R/refmans/stats/html/sd.html)', 'Standard deviation',
  '[`search`](https://search.r-project.org/R/refmans/base/html/search.html)', 'Search path',
  '[`seed`, `set.seed`](https://search.r-project.org/R/refmans/base/html/Random.html)', 'Random number generation seed',
  '[`seq`](https://search.r-project.org/R/refmans/base/html/seq.html)', 'Sequence generation',
  '[`skewness`](https://search.r-project.org/CRAN/refmans/e1071/html/skewness.html)', 'Skewness',
  '[`sort`](https://search.r-project.org/R/refmans/base/html/sort.html)', 'Sorting vectors',
  '[`summary`](https://search.r-project.org/R/refmans/base/html/summary.html)', 'Summaries of an `R` object',
  '[`t.test`](https://search.r-project.org/R/refmans/stats/html/t.test.html)', 'Student\'s $t$-test',
  '[`table`](https://search.r-project.org/R/refmans/base/html/table.html)', 'Cross tabulation',
  '[`uniroot`](https://search.r-project.org/R/refmans/stats/html/uniroot.html)', 'One dimensional root-finding',
  '[`var`](https://search.r-project.org/R/refmans/stats/html/cor.html)', 'Variance',
  '[`var.test`](https://search.r-project.org/R/refmans/stats/html/var.test.html)', '$F$-test to compare variances',
  '[`with`, `within`](https://search.r-project.org/R/refmans/base/html/with.html)', 'Evaluate an expression in a data environment', 
  '[`xtabs`](https://search.r-project.org/R/refmans/stats/html/xtabs.html)', 'Cross tabulation'
) |>
  matrix(nrow = 2L, dimnames = list(c('Term / Abbreviation', 'Description'), NULL)) |>
  t.default() |>
  as.data.frame.matrix() |> 
  kable() 
```

# Function `paths_function()`

## Normal Distribution


```{r}
#| fig-width: 5
#| fig-height: 3
ggplot() + 
  paths_function(fun = dnorm, dots = list(mean = 1:0), hjust = .4) + 
  xlim(-3, 4)
```


```{r}
#| fig-width: 5
#| fig-height: 3
ggplot() + 
  paths_function(
    fun = dnorm, dots = list(mean = 0, sd = c(1, 1.3)), 
    aes_ = c('color', 'linetype'), size = 3
  ) + 
  xlim(-3, 3)
```

## $t$-Distribution
```{r}
#| fig-width: 5
#| fig-height: 3
ggplot() + 
  paths_function(fun = dt, dots = list(df=c(1,2,5,Inf)), size = 2.5) +
  xlim(-4,4)
```


## $\chi^2$-Distribution
```{r}
#| fig-width: 5
#| fig-height: 3
ggplot() + 
  paths_function(
    fun = dchisq, dots = list(df = c(1,3,5,10)), 
    hjust = c(.2,.25,.5,.55), size = 3
  ) + 
  xlim(.2,8)
```

## $\gamma$-Distribution

```{r}
#| fig-width: 5
#| fig-height: 3
ggplot() + 
  paths_function(fun = dgamma, dots = list(shape = 1:4), hjust = .15, size = 3) + 
  xlim(0, 5)
```

# Function `paths_discrete()`

## Poisson Distribution

```{r}
#| fig-width: 5
#| fig-height: 3
ggplot() + 
  paths_discrete(dpois, dots = list(lambda = 5:10), hjust = .3, xlim = 20L)
```


## Negative Binomial Distribution

```{r}
#| fig-width: 5
#| fig-height: 3
ggplot() + 
  paths_discrete(fun = dnbinom, dots = list(size = 1:3, prob = .3), xlim = 25L)
```

```{r}
#| fig-width: 5
#| fig-height: 3
ggplot() + 
  paths_discrete(
    fun = dnbinom, dots = list(size = 3, prob = seq.int(.15, .25, by = .05)), 
    hjust = .2, xlim = 40L
  )
```



## Generalized Poisson Distribution

```{r}
library(VGAM)
```


```{r}
ggplot() + 
  paths_discrete(dgenpois1, dots = list(meanpar = 1:3), xlim = 10L)
```


```{r}
ggplot() + 
  paths_discrete(dgenpois1, dots = list(meanpar = 2, dispind = 1:3), xlim = 10L, size = 2L)
```

