---
title: "gg.tzh"
author: Tingting Zhan
format: 
  html:
    page-layout: full
    html-math-method: katex
toc: true
toc-location: left
toc-depth: 4
toc-title: ''
editor: visual
knitr:
  opts_chunk: 
    collapse: true
    comment: "#>" 
vignette: >
  %\VignetteIndexEntry{intro}
  %\VignetteEngine{quarto::html}
  %\VignetteEncoding{UTF-8}
---

# Introduction

This vignette of package **`gg.tzh`** ([Github](https://github.com/tingtingzhan/gg.tzh)) documents ...

## Note to Students

Examples in this vignette require that the `search` path has

```{r}
library(gg.tzh)
library(ggplot2)
library(geomtextpath)
library(scales)
library(latex2exp)
```

```{r}
#| echo: false
library(knitr) # for tables in this vignette
#options(mc.cores = 1L) # for CRAN submission
theme_bw() |> theme_set()
```

## Terms and Abbreviations

| Term / Abbreviation | Description |
|------------------------------------|------------------------------------|
| [`|>`](https://search.r-project.org/R/refmans/base/html/pipeOp.html) | Forward pipe operator introduced since `R` 4.1.0 |
| `$` | [Extract](https://search.r-project.org/R/refmans/base/html/Extract.html) parts of an object |
| `CRAN`, `R` | [The Comprehensive R Archive Network](https://cran.r-project.org) |
| [`class`](https://search.r-project.org/R/refmans/base/html/class.html) | Object class |
| [`dbinom`, `pbinom`, `qbinom`](https://search.r-project.org/R/refmans/stats/html/Binomial.html) | Binomial density, probability, quantile |
| [`dpois`, `ppois`, `qpois`](https://search.r-project.org/R/refmans/stats/html/Poisson.html) | Poisson density, probability, quantile |
| [`dnorm`, `pnorm`, `qnorm`](https://search.r-project.org/R/refmans/stats/html/Normal.html) | Normal density, probability, quantile |
| [`L`](https://adv-r.hadley.nz/vectors-chap.html#atomic-vectors) | [Integer](https://search.r-project.org/R/refmans/base/html/integer.html) notation |
| [`label_percent`](https://search.r-project.org/CRAN/refmans/scales/html/label_percent.html) | Label for percentages |
| [`search`](https://search.r-project.org/R/refmans/base/html/search.html) | Search path |

# Function `paths_function()`

## Normal Distribution

```{r}
#| fig-width: 5
#| fig-height: 3
ggplot() + 
  paths_function(fun = dnorm, dots = list(mean = 1:0), hjust = .4) + 
  xlim(-3, 4)
```

```{r}
#| fig-width: 5
#| fig-height: 3
ggplot() + 
  paths_function(
    fun = pnorm, dots = list(mean = 0, sd = c(1, 2)), 
    aes_ = c('color', 'linetype'), hjust = .3, size = 3
  ) + 
  scale_y_continuous(label = label_percent()) +
  xlim(-3, 3)
```

## $t$-Distribution

```{r}
#| fig-width: 5
#| fig-height: 3
ggplot() + 
  paths_function(fun = dt, dots = list(df = c(1,2,5,Inf)), size = 2.5) +
  xlim(-4, 4)
```

## $\chi^2$-Distribution

```{r}
#| fig-width: 5
#| fig-height: 3
ggplot() + 
  paths_function(
    fun = dchisq, dots = list(df = c(1,3,5,10)), 
    hjust = c(.2,.25,.5,.55), size = 3
  ) + 
  xlim(.2, 8)
```

## $\gamma$-Distribution

```{r}
#| fig-width: 5
#| fig-height: 3
ggplot() + 
  paths_function(fun = dgamma, dots = list(shape = 1:4), hjust = .15, size = 3) + 
  xlim(0, 5)
```

# Function `paths_discrete()`

## Poisson Distribution

```{r}
#| fig-width: 5
#| fig-height: 3
ggplot() + 
  paths_discrete(dpois, dots = list(lambda = 5:10), hjust = .3, xlim = 20L)
```

## Negative Binomial Distribution

```{r}
#| fig-width: 5
#| fig-height: 3
ggplot() + 
  paths_discrete(fun = dnbinom, dots = list(size = 1:3, prob = .3), xlim = 25L)
```

```{r}
#| fig-width: 5
#| fig-height: 3
ggplot() + 
  paths_discrete(
    fun = dnbinom, dots = list(size = 3, prob = seq.int(.15, .25, by = .05)), 
    hjust = .2, xlim = 40L
  )
```

## Generalized Poisson Distribution

```{r}
ggplot() + 
  paths_discrete(VGAM::dgenpois1, dots = list(meanpar = 1:3), xlim = 10L)
```

```{r}
ggplot() + 
  paths_discrete(VGAM::dgenpois1, dots = list(meanpar = 2, dispind = 1:3), xlim = 10L, size = 2L)
```
